style_template

### 2021-12-07 products/style_template.Rmd
Manuscript Edits - CC

---
title: "Relationship Between Common Stream Health Indicators"
subtitle: ""
author: Carter Coleman
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2:
    reference_docx: ../style_template.docx 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../MADA.bib
csl: ../elsevier_style.csl
---

>>>>

---
title: "style_template"
author: "C. Coleman"
date: "11/28/2021"
output: word_document
---
